Case Study (McKenna)

### 2020-07-03 Cases/mrp/Case Study (McKenna) .Rmd
Wokring on Postratification

# Importing the data. 
sample <- read_csv(here::here("code", "mrp", "data", "sample.csv"))
proststrat <- read_csv(here::here("code", "mrp", "data", "poststrat.csv"))
true_popn <- read_csv(here::here("code", "mrp", "data", "true_popn.csv"))
```

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)
```

@@

```{r}
# Observations. 
downes_list <- list(
  outcome = sample$service_failure,
  male = sample$male + 1,
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income,
  state = sample$state,
  n = length(sample$service_failure), 
  n_male = max(sample$male) + 1,
  n_age = max(sample$age),
  n_eth = max(sample$eth),
  n_income = max(sample$income),
  n_state = max(sample$state)
)
```

@@

>>>>

# Importing the data. 
sample <- read_csv(here::here("data", "sample.csv"))
proststrat <- read_csv(here::here("data", "poststrat.csv"))
true_popn <- read_csv(here::here("data", "true_popn.csv"))
```

@@

```{r, eval = FALSE}
fit <- stan(
  file = here::here("Code", "mrp", "logit_hier.stan"),
  data = data_list,
  seed = 42 
)

fit
```

```{r, eval = FALSE}
posterior_prob <- posterior_linpred(fit, transform = TRUE, newdata = poststrat)
poststrat_prob <- posterior_prob %*% poststrat$N / sum(poststrat$N)
model_popn_pref <- c(mean = mean(poststrat_prob), sd = sd(poststrat_prob))
round(model_popn_pref, 3)

true_popn_pref <- sum(true_popn$satisfaction * poststrat$N) / sum(poststrat$N)
round(true_popn_pref, 3)

state_df <- data.frame(
  State = 1:50,
  model_state_sd = rep(-1, 50),
  model_state_pref = rep(-1, 50),
  sample_state_pref = rep(-1, 50),
  true_state_pref = rep(-1, 50),
  N = rep(-1, 50)
)

for(i in 1:length(levels(as.factor(poststrat$state)))) {
  poststrat_state <- poststrat[poststrat$state == i, ]
    posterior_prob_state <- posterior_linpred(
    fit,
    transform = TRUE,
    draws = 1000,
    newdata = as.data.frame(poststrat_state)
  )
  poststrat_prob_state <- (posterior_prob_state %*% poststrat_state$N) / sum(poststrat_state$N)
  #This is the estimate for popn in state:
  state_df$model_state_pref[i] <- round(mean(poststrat_prob_state), 4)
  state_df$model_state_sd[i] <- round(sd(poststrat_prob_state), 4)
  #This is the estimate for sample
  state_df$sample_state_pref[i] <- round(mean(sample$cat_pref[sample$state == i]), 4)
  #And what is the actual popn?
  state_df$true_state_pref[i] <-
    round(sum(true_popn$cat_pref[true_popn$state == i] * poststrat_state$N) /
            sum(poststrat_state$N), digits = 4)
  state_df$N[i] <- length(sample$satisfaction[sample$state == i])
}

state_df[c(1,3:6)]
```

@@

```{r}
# Observations. 
downes_list <- list(
  outcome = sample$service_failure,
  male = sample$male + 1,
  age = sample$age, 
  eth = sample$eth, 
  income = sample$income,
  state = sample$state,
  n = length(sample$service_failure), 
  n_male = max(sample$male) + 1,
  n_age = max(sample$age),
  n_eth = max(sample$eth),
  n_income = max(sample$income),
  n_state = max(sample$state)
)

  n_iter <- 1000
  n_chain <- 1
  n_sim <- (n_iter * n_chain)/2 
```

@@

```{r, eval = FALSE}

  stanfit_final_sim <- extract(fit, pars=c("b0","a_income","a_age","a_eth","a_state","a_male","sigma_age","sigma_eth","sigma_income", "sigma_male","sigma_state"))

n_pscell <- length(poststrat$N)
n_state <- max(poststrat$state)

stanfit_final_ypred <- array(NA, c(n_sim, n_pscell))
  for(l in 1:n_pscell){
    stanfit_final_ypred[,l] <- invlogit(stanfit_final_sim$b0 + 
                                        stanfit_final_sim$a_age * poststrat$age[l] +
                                        stanfit_final_sim$a_income * poststrat$income[l] +
                                        stanfit_final_sim$a_eth * poststrat$eth[l] +
                                        stanfit_final_sim$a_state * poststrat$state[l] +
                                        stanfit_final_sim$a_male * poststrat$male[l])
  }

  stanfit_final_ps <- c(NA, n_sim)
  for(s in 1:n_sim){
    stanfit_final_ps[s] <- sum(poststrat$N*stanfit_final_ypred[s,])/sum(poststrat$N)
  }

stanfit_final_q <- round(quantile(stanfit_final_ps, c(0.025,0.50,0.975)),3)
  stanfit_final_sd <- round(sd(stanfit_final_ps),4)
  stanfit_final_pop_est <- cbind(stanfit_final_q[2], stanfit_final_sd, stanfit_final_q[1],
                                 stanfit_final_q[3])

```
